Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Update paper.

```{r}
#| include: false
#| warning: false
#| message: false
options(repos = c(CRAN = "https://cloud.r-project.org"))
library(tidyverse)
library(readr)
library(here)
library(knitr)
library(kableExtra)
library(scales)
install.packages("arrow")
library(arrow)
library(bayesplot)
library(rstanarm)

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(readr)
library(here)
library(knitr)
library(kableExtra)
library(scales)
library(arrow)
library(bayesplot)
library(rstanarm)
